Estimating duration in the presence of misclassification

### 2024-01-29 transmission.tex

In this chapter, I use the preferred estimate of the duration of PCR positivity (see \cref{E-imperf-test:sec:conclusion}) to estimate the transmission of SARS-CoV-2 in England.
This estimation is based on the CIS data (see \cref{transmission:sec:data} for further details).
Estimating transmission is the ultimate aim of this thesis.

I take two approaches; the theoretical advantages of each were discussed in \cref{E-inc-prev:sec:infection-process}.
First, in \cref{backcalc}, I use a backcalculation approach, based on \cref{E-inc-prev:eq:EPt}.
Then, in \cref{SEIR}, I use a mechanistic compartmental model, an implementation of the model introduced in \cref{E-SEIR:sec:mechanistic-models}.
Finally, in \cref{transmission:sec:comparison}, I compare the results of the two approaches.

@@

\todo[inline]{Consider moving all of this section into chapter 2, where CIS is introduced}

>>>>

In this chapter, I use the preferred estimate of the duration of PCR positivity (see \cref{E-imperf-test:sec:conclusion}) to estimate the transmission of SARS-CoV-2 in England.
This estimation is based only on the CIS data (see \cref{transmission:sec:data} for further details).
I will show that this data is sufficient to estimate the parameters of the transmission process, suggesting surveys of this type are sufficient for surveillance of an epidemic.

I take two approaches; the theoretical advantages of each were discussed in \cref{E-inc-prev:sec:infection-process}.
First, in \cref{backcalc}, I use a backcalculation approach, based on \cref{E-inc-prev:eq:EPt}.
This approach enables estimation of incidence within (sub)populations of England.
Then, in \cref{SEIR}, I use a mechanistic compartmental model, an implementation of the model introduced in \cref{E-SEIR:sec:mechanistic-models}.
In addition to estimating incidence, this approach also estimates the components of transmission, \eg whether changes can be explained by changes in contact rates.
Finally, in \cref{transmission:sec:comparison}, I compare the results of the two approaches.

@@

\todo[inline]{Consider moving all of this section into chapter 2, where CIS is introduced, and spell it out a bit more in that context}
